Effects of Reynolds Number on the Performance and Near-Wake Dynamics of a Vertical-Axis Cross-Flow Turbine

### 2015-04-23 paper.tex
Work on introduction

Scaled physical models are often used in science and engineering to approximate
real-world systems. However, the principle of dynamic similarity allows for
geometrically scaled systems to be dynamically identical in scale if certain
nondimensional physical parameters are matched. In the case of fluid systems,
the most important parameter is often the Reynolds number, which quantifies the
importance of viscosity on the flow. As such, hereafter we will use the word
``scale'' to refer to this dynamical scale rather than the geometric scale.

@@

When designing or studying arrays, it is common to use very small
(geometrically) scaled devices. 
% %
\todo[inline]{Get a reference for this, and a sample geometric scale.} 
% %
Sometimes these are not even models of turbines, but
wake generating objects, e.g., porous disks, that are meant to replicate the
wakes of real turbines. In this case, it is of interest to determine at what
scale one might be able to realistically study wake flows in an array, and also
to evaluate the effectiveness of a wake generator. In other words, a wake
generator may do a fine job simulating a scaled turbine, but how well can it
simulate a real turbine?

>>>>

Scaled physical models are often used in science and engineering to approximate
real-world systems. However, the principle of dynamic similarity allows for
geometrically scaled systems to be dynamically identical in scale if certain
nondimensional physical parameters are matched. In the case of fluid systems,
the most important parameter is often the Reynolds number, which quantifies the
importance of viscosity on the flow physics. As such, hereafter we will use the
word ``scale'' to refer to this dynamical scale rather than the geometric scale.

@@

When designing or studying arrays, it is common to use very small
(geometrically) scaled devices \cite{Chamorro2011, Chamorro2011b}. It is
therefore important to realize the limitations of evaluating both the power
output of turbines and the wake recovery when Reynolds number is very far from
full scale. Sometimes models used are not turbines, but wake generating objects,
e.g., porous disks, that are meant to replicate the wakes of real turbines
\cite{Goldenberg1983}. In this case, it is of interest to determine at what
scale one might be able to realistically study wake flows in an array, and also
to evaluate the effectiveness of a wake generator. In other words, a wake
generator may do a fine job simulating a scaled turbine, but how well can it
simulate a full-scale device?
